Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
editing

    item_PF = paste(`Course ID`, PF, sep = "_"),
    item_HL = paste(`Course ID`, HL, sep = "_"),
    item_Grade = paste(`Course ID`, round(Grade,0), sep = "_")
    ) %>%
  rename(
    item = `Course ID`
  )
```

@@

    item_PF = paste(item, PF, sep = "_"),
    item_HL = paste(item, HL, sep = "_"),
    item_Grade = paste(item, Grade_round, sep = "_")
    )
```
### Transactions for Apriori
```{r making transactions}

>>>>

    item_PF = paste(`Course ID`, PF, sep = "_"),
    item_HL = paste(`Course ID`, HL, sep = "_"),
    item_Grade = paste(`Course ID`, round(Grade,0), sep = "_")
    ) %>%
  rename(
    item = `Course ID`
  )

```

@@

    item_PF = paste(item, PF, sep = "_"),
    item_HL = paste(item, HL, sep = "_"),
    item_Grade = paste(item, Grade_round, sep = "_")
    )
```

```{r}
d_support <- d_transactions %>%
  mutate(
    grade_round = round(Grade)
  ) %>%
  group_by(
    item
    ) %>%
  summarise(
    rate.fail = mean(PF == "fail"),
    rate.low  = mean(HL == "low"),
    rate.0    = mean(grade_round == 0),
    # continue with other grades
    )
```

### Transactions for Apriori
```{r making transactions}
